Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-09-23 manuscript.Rmd
distinguish exploration

The convenient comparison of preregistration and publication with PAC is particularly noteworthy.
Because there is a single "source of truth", the dynamic document including code, under version control, changes can be inspected by reader and authors alike.
To make the comparison easier, we highly recommend that the authors review all changes to summarize and justify them for their reader [^summarize-changes].
The reader is also in a position to inspects the changes and can therefore make an informed judgment about accepting or rejecting the justifications.

Deviations from the preregistration are sometimes demonized as if encountering unexpected aspects would invalidate a whole carefully crafted study.
We, however, oppose this view.
The problem is not deviating from the preregistration; it is not making these changes transparent.
In fact, we expect that most PACs will require changes after the researcher collects data.
And often deviations provide opportunity to learn from the unexpected.
Another reason why transparency is important in this regard, is that an empirical test of an theory can not test the theory alone but tests it in conjunction with auxiliary assumption [@meehlTheoreticalRisksTabular1978].

Take the following example: A preregistration intended to include "working memory" and "fluid intelligence" as predictors for reaction time in an experiment.
However, after fitting the model on the actual data both constructs exhibit high collinearity.
The authors decide that for their purpose, these variables are interchangeable and remove one.
For them, this change simply does not affect their theory's core but was an auxiliary assumption, and they might be right.
Another researcher, however, who, e.g. hopes to incorporate their results into a theory about intelligence, might disagree about the importance of this assumption and would accordingly view the finding as more explorative because of the change to the preregistrations.
In other words, "one man's trash is another man's treasure".

@@

Another common misunderstanding is that, preregistration, and therefore PAC, preclude exploratory analyses.
Again such exploratory results should merely be explicitly declared in the manuscript to allow appropriate judgment of the results.
In fact, PAC allows to preregister exploratory statistical models.
Such preregistration communicates clearly how much exploration was going on, an information that is crucial for assessing the uncertainty of such results.

>>>>

The convenient comparison of preregistration and publication with PAC is particularly noteworthy.
Because there is a single "source of truth", the dynamic document including code, under version control, changes can be inspected by reader and authors alike.
To make the comparison easier, we highly recommend that the authors review all changes to summarize and justify them for their reader e.g. in the discussion [^summarize-changes].
The reader is also in a position to inspects the changes and can therefore make an informed judgment about accepting or rejecting the justifications.

Deviations from the preregistration are sometimes demonized as if encountering unexpected aspects would invalidate a whole carefully crafted study.
We, however, oppose this view.
The problem is not deviating from the preregistration; it is not making these changes transparent.
In fact, we expect that most PACs will require changes after the researcher collects data.
Often deviations provide opportunity to learn from the unexpected.
Transparency is important in this regard because an empirical test of a theory can not test the theory alone but tests it in conjunction with auxiliary assumption [@meehlTheoreticalRisksTabular1978].

Take the following example: A preregistration intended to include "working memory" and "fluid intelligence" as predictors for reaction time in an experiment.
However, after fitting the model on the actual data both constructs exhibit high collinearity.
The authors decide that for their purpose, these variables are interchangeable and remove one.
For them, this change simply does not affect their theory's core but was an auxiliary assumption, and they might be right.
Another researcher, however, who, e.g. hopes to incorporate exactly this result into a theory about intelligence, might disagree about the importance of this assumption and would accordingly view the finding as more explorative because of the change to the preregistrations.
In other words, "one man's trash is another man's treasure".

@@

Another common misunderstanding is that, preregistration, and therefore PAC, preclude exploratory analyses.
We must differentiate here between two kinds of exploration.
First, the traditional meaning of ad hoc statistical procedures and post hoc explanation of the results.
Such traditional exploratory results should merely be explicitly declared in the manuscript to allow appropriate judgment of the results.
The second kind of exploration is that through procedural well defined exploration in the form of exploratory statistical models that are common in machine learning.
Somewhat ironically, PAC enables preregistration of such procedures and offers the merit to communicate precisely how much exploration was done; an information that is crucial for assessing the uncertainty of such "preregisterable" but exploratory results.
